Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-14 Manuscript/sec4-experiments.tex
修改sec4一些图

\begin{figure}
	\centering
    \subfloat[pubmed\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.png}}
    \subfloat[amazon-photo\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.png}}
    \subfloat[coauthor-physics\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.png}} \\
    \subfloat[amazon-computers\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.png}}
    \subfloat[flickr\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.png}}
    \subfloat[com-amazon\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.png}}
    \caption{Different Datasets's absolute training time per epoch in four GNN models. (total 50 epochs)}
	\label{fig:exp_absolute_training_time}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}
    \caption{GCN}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}
    \caption{GGNN}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}
    \caption{GAT}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}
    \caption{GaAN}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
    \caption{The memory Usage of each GNN Model in different hyperparameter}
	\label{fig:exp_hyperparameter_memory_usage}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gat.png}}
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gaan.png}}
    \caption{The vertex calculation and edge calculation of each GNN Model}
	\label{fig:exp_vertex_edge_cal_proportion}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gat.png}}
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.png}}
    \caption{The vertex calculation and edge calculation of each GNN Model}
	\label{fig:exp_avg_degree_on_vertex_edge_cal_time}
\end{figure}

\paragraph{Time-consuming decomposition analysis of edge calculation}
The edge calculation phase can be further decomposed into four steps of collect, message, aggregate and update,
as shown in Fig~\ref{fig:steps_in_edge_calculation}. The figure shows the $l$ layer The edge calculation process of GNN.
edge index is a matrix that holds the size of the edge set of the graph as $M*2$, where $M$ is the number of edges of the graph,
and the two columns of the matrix respectively store the source vertex and the target vertex of each edge.
The edge index remains unchanged throughout the calculation process.
The collect step is used to prepare the data structure required for edge calculation.
This step will input the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \ leq N)$
is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the input edge calculation function $\phi$
(including $\boldsymbol{h}_i^l$,$\boldsymbol{h}_j^ l$ and $\boldsymbol{e}_{j, i}^l$).
There is no calculation in this step, only data access is involved. The message step calls the function given by the user $\phi$ to
complete the edge calculation process, and get each The message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
The aggregate step is based on the target of each edge, the message vector with the same target vertex is aggregated by the aggregation operator $\Sigma$,
and each vertex aggregation vector $\boldsymbol{a}_i^l (1 \leq i \leq N)$ is obtained. 
The last update The step is optional, and it can perform additional correction processing on the aggregated vector (for example, adding bias to GCN).
The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ As an input parameter.

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
    \caption{Steps in edge calculation}
    \label{fig:steps_in_edge_calculation}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gat.png}}
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.png}}
    \caption{The vertex calculation and edge calculation of each GNN Model}
	\label{fig:exp_edge_calc_decomposition}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_usage_stage_amp.png}
    \caption{Figure: Maximum memory usage in each stage. Data Load refers to memory usage after data is loaded. Data set: amp. Other datasets are similar}
    \label{fig:exp_memory_usage_stage_amp}
\end{figure}

@@

Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
Because the input feature dimension of the cph data set is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
of the graph is much higher than the matrix size of the intermediate calculation result of the cache, 
so its expansion ratio is particularly low, and the cam data set is the opposite. In order to measure the effect of the input feature vector dimension on the memory
expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
Fig~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
\textbf{In the same GNN structure and hyperparameter settings, using a higher-dimensional input feature vector can reduce memory expansion ratio} .

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.png}
    \caption{The change of the memory expansion ratio with the dimension of the input feature vector. Data set: cam, other datasets are similar}
    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
\end{figure}

@@

In the current implementation of PyG, the GNN model parameters always reside on the GPU,
and the data set resides in the main memory. When processing each epoch, the CPU samples
the graph data set in the main memory and generates several batches,
Each batch is a small-scale subgraph of the data set. When training each batch, 
PyG copies the subgraph data corresponding to the batch to the GPU's memory,
trains based on the subgraph and updates the model parameters according to the gradient.
Based on the sampling technology and SGD optimization technology, 
the evaluation of the model parameters is performed every several epochs. 
The evaluation can be carried out on the CPU or on the GPU. 
Therefore, the statistical data in the experiments in this section does not include the evaluation phase. 
Neighbor is selected in this section Sampler and cluster sampler are two typical graph sampling techniques for analysis.

Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraphs sampled in the two sampling techniques varies with the batch size.
For the neighbor sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of points.
For cluster sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole image.
\textbf{neighbor sampler is very sensitive to the increase in batch size*. As the batch size increases, 
the sampling sub-graph The number of vertices/edges and the average degree both increase rapidly and tend to stabilize}.
\textbf{cluster sampler is less sensitive to the increase in batch size*, the number of vertices/average degree increases
linearly with the increase in batch size, and the number of edges is in the batch When the size is relatively small,
it also increases linearly.}

It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole picture,
especially when the relative batch size is low}. Taking the neighbor sampler at a relative batch size of 6\% as an example,
The average degree of the amp dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
which is much lower than the average degree of the full picture;
the average degree of the subgraphs sampled by the cluster sampler is lower, only 3.0.
Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled sub-graphs with the original image.
The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
The reason is that the distribution of vertices in the actual graph data set follows a power-rate distribution, and a small number of vertices The degree is very high,
which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraphs will increase the time-consuming
proportion of point calculation. For GGNN with high point calculation complexity, point calculation will replace edge calculation and become a performance bottleneck.

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_graphsage_gcn.png}}
    \subfloat[Cluster Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_cluster_gcn.png}}
    \caption{The size of the sampled subgraph changes with the batch size. Each batch size is sampled 50 times, and the error bar represents the standard deviation. The relative batch size is the ratio relative to the full image.)}
    \label{fig:exp_sampling_minibatch_graph_info}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.png}
    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. Data set: amp. Batch size = 512 (neighbor sampler) / 20 (cluster sampler)}
    \label{fig:exp_sampling_minibatch_degrees_distribution}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.png}}
    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}}
    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.png}}
    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.png}}
    \caption{The training time of each batch changes with the batch size. FULL means that the full image participates in the training phase (excluding evaluation).}
    \label{fig:exp_sampling_batch_train_time}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.png}}
    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}}
    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.png}}
    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.png}}
    \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}
    \label{fig:exp_sampling_batch_train_time}
\end{figure}
\label{sec:effects_of_sampling_techniques_on_performance}

>>>>

\begin{figure}
	\centering
    \subfloat[pubmed\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.png}}
    \subfloat[amazon-photo\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.png}}
    \subfloat[coauthor-physics\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.png}} \\
    \subfloat[amazon-computers\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.png}}
    \subfloat[flickr\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.png}}
    \subfloat[com-amazon\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.png}}
    \caption{The impact of training time}
	\label{fig:exp_absolute_training_time}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}}\\
    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}}\\
    \subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}}\\
    \subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}}
    \caption{The influence of hyperparameters on GNN vertex/edge calculation time}
	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
\end{figure}

@@

@@

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
    \caption{The effect of hyperparameters on GPU memory usage during the training phase (excluding the dataset itself)}
	\label{fig:exp_hyperparameter_memory_usage}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gat.png}}
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gaan.png}}
    \caption{Vertex/edge calculation time-consuming ratio.}
	\label{fig:exp_vertex_edge_cal_proportion}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gat.png}}
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.png}}
    \caption{The effect of the average vertex degree on the time-consuming proportion of vertex/edge calculation.}
	\label{fig:exp_avg_degree_on_vertex_edge_cal_time}
\end{figure}

\paragraph{Time-consuming decomposition analysis of edge calculation}
The edge calculation phase can be further decomposed into four steps of collect, message, aggregate and update,
as shown in Fig~\ref{fig:steps_in_edge_calculation}. The figure shows the $l$ layer The edge calculation process of GNN.
edge index is a matrix that holds the size of the edge set of the graph as $M*2$, where $M$ is the number of edges of the graph,
and the two columns of the matrix respectively store the source vertex and the target vertex of each edge.
The edge index remains unchanged throughout the calculation process.
The collect step is used to prepare the data structure required for edge calculation.
This step will input the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the input edge calculation function $\phi$
(including $\boldsymbol{h}_i^l$,$\boldsymbol{h}_j^ l$ and $\boldsymbol{e}_{j, i}^l$).
There is no calculation in this step, only data access is involved. The message step calls the function given by the user $\phi$ to
complete the edge calculation process, and get each The message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
The aggregate step is based on the target of each edge, the message vector with the same target vertex is aggregated by the aggregation operator $\Sigma$,
and each vertex aggregation vector $\boldsymbol{a}_i^l (1 \leq i \leq N)$ is obtained. 
The last update The step is optional, and it can perform additional correction processing on the aggregated vector (for example, adding bias to GCN).
The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ As an input parameter.

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
    \caption{Step decomposition of edge calculation}
    \label{fig:steps_in_edge_calculation}
\end{figure}

@@

\begin{figure}
	\centering
    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gcn.png}}
    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_ggnn.png}}\\
    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gat.png}}
    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.png}}
    \caption{Time-consuming decomposition of edge calculations (including Layer0 and Layer1).}
	\label{fig:exp_edge_calc_decomposition}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_usage_stage_amp.png}
    \caption{Maximum memory usage in each stage. Data Load refers to memory usage after data is loaded. dataset: amp. Other datasets are similar}
    \label{fig:exp_memory_usage_stage_amp}
\end{figure}

@@

Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
Because the input feature dimension of the cph dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
of the graph is much higher than the matrix size of the intermediate calculation result of the cache, 
so its expansion ratio is particularly low, and the cam dataset is the opposite. In order to measure the effect of the input feature vector dimension on the memory
expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
Fig~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
\textbf{In the same GNN structure and hyperparameter settings, using a higher-dimensional input feature vector can reduce memory expansion ratio} .

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.png}
    \caption{The change of the memory expansion ratio with the dimension of the input feature vector. dataset: cam, other datasets are similar}
    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
\end{figure}

@@

In the current implementation of PyG, the GNN model parameters always reside on the GPU,
and the dataset resides in the main memory. When processing each epoch, the CPU samples
the graph dataset in the main memory and generates several batches,
Each batch is a small-scale subgraph of the dataset. When training each batch, 
PyG copies the subgraph data corresponding to the batch to the GPU's memory,
trains based on the subgraph and updates the model parameters according to the gradient.
Based on the sampling technology and SGD optimization technology, 
the evaluation of the model parameters is performed every several epochs. 
The evaluation can be carried out on the CPU or on the GPU. 
Therefore, the statistical data in the experiments in this section does not include the evaluation phase. 
Neighbor is selected in this section Sampler and cluster sampler are two typical graph sampling techniques for analysis.

Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraphs sampled in the two sampling techniques varies with the batch size.
For the neighbor sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of verticess.
For cluster sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole image.
\textbf{neighbor sampler is very sensitive to the increase in batch size*. As the batch size increases, 
the sampling sub-graph The number of vertices/edges and the average degree both increase rapidly and tend to stabilize}.
\textbf{cluster sampler is less sensitive to the increase in batch size*, the number of vertices/average degree increases
linearly with the increase in batch size, and the number of edges is in the batch When the size is relatively small,
it also increases linearly.}

It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole picture,
especially when the relative batch size is low}. Taking the neighbor sampler at a relative batch size of 6\% as an example,
The average degree of the amp dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
which is much lower than the average degree of the full picture;
the average degree of the subgraphs sampled by the cluster sampler is lower, only 3.0.
Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled sub-graphs with the original image.
The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
The reason is that the distribution of vertices in the actual graph dataset follows a power-rate distribution, and a small number of vertices The degree is very high,
which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraphs will increase the time-consuming
proportion of vertex calculation. For GGNN with high vertex calculation complexity, vertex calculation will replace edge calculation and become a performance bottleneck.

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_graphsage_gcn.png}} \\
    \subfloat[Cluster Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_cluster_gcn.png}}
    \caption{The size of the sampled subgraph changes with the batch size. Each batch size is sampled 50 times, and the error bar represents the standard deviation. The relative batch size is the ratio relative to the full image.)}
    \label{fig:exp_sampling_minibatch_graph_info}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.png}
    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. dataset: amp. Batch size = 512 (neighbor sampler) / 20 (cluster sampler)}
    \label{fig:exp_sampling_minibatch_degrees_distribution}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.png}}
    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}} \\
    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.png}}
    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.png}}
    \caption{The training time of each batch changes with the batch size. FULL means that the full image participates in the training phase (excluding evaluation).}
    \label{fig:exp_sampling_batch_train_time}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.png}}
    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}} \\
    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.png}}
    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.png}}
    \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}
    \label{fig:exp_sampling_memory_usage}
\end{figure}
\label{sec:effects_of_sampling_techniques_on_performance}
